Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-16 krs-survey.tex
Reorder reviews in alphabetical order

\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & {\bf Reasoner} & Main reference \\
\midrule
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & KRS & Mavridis, Roy \par (MIT MediaLab) & & ? & & & \cite{Mavridis2006} \\
OUR-K & KRS & Suh et al. \par (Hanyang Univ.) & \url{incorl.hanyang.ac.kr/xe} & ? & Horn Clauses & ? & \cite{Suh2007} \\
Ke Jia Project & KRS & Chen et al. \par (Univ. of Science and Technology of China) & \url{www.wrighteagle.org/en} & ASP & ASP & ASP & \cite{Chen2010} \\
ARMAR/Tapas & KRS & Holzapfel, Waibel \par (Karlsruhe TH) & & ? & TFS (Typed Feature Structures) & & \cite{Holzapfel2008}\\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
OBOC & KRS & Mendoza & & & & & \cite{Mendoza2005} \\
% & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\ % -> affordances, but no implementation on a robot
% & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\ % -> mostly planning under uncertainty
% & & Hertzberg (Osnabrück Univ.) \\ % -> affordances, semantic mapping
% (based on {\sc KnowRob} & & (JSK) \\

@@

\fxfatal{Bielefeld -> could not find much\ldots}
\fxfatal{Kollar/Tellex -> really focusing on the natural language grounding}

@@

@@

    \caption{OUR-K organizes knowledge into fives \emph{classes}, each composed
    of \emph{levels}. Figure based on~\ref{Lim2011}.}

>>>>

\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & {\bf Reasoner} & Main reference \\
\midrule
ARMAR/Tapas & KRS & Holzapfel, Waibel \par (Karlsruhe TH) & & ? & TFS (Typed Feature Structures) & & \cite{Holzapfel2008}\\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
GSM & KRS & Mavridis, Roy \par (MIT MediaLab) & & ? & & & \cite{Mavridis2006} \\
Ke Jia Project & KRS & Chen et al. \par (Univ. of Science and Technology of China) & \url{www.wrighteagle.org/en} & ASP & ASP & ASP & \cite{Chen2010} \\
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
%OBOC & KRS & Mendoza & & & & & \cite{Mendoza2005} \\
OUR-K & KRS & Suh et al. \par (Hanyang Univ.) & \url{incorl.hanyang.ac.kr/xe} & ? & Horn Clauses & ? & \cite{Suh2007} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
%Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
% & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\ % -> affordances, but no implementation on a robot
% & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\ % -> mostly planning under uncertainty
% & & Hertzberg (Osnabrück Univ.) \\ % -> affordances, semantic mapping
% (based on {\sc KnowRob} & & (JSK) \\

@@

%\fxfatal{Bielefeld -> could not find much\ldots}
%\fxfatal{Kollar/Tellex -> really focusing on the natural language grounding}

\subsection{GOLOG}
\label{sect|kejia}

@@

    \caption{OUR-K organizes knowledge into fives \emph{classes}, each composed
    of \emph{levels}. Figure based on~\cite{Lim2011}.}

@@
